A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-21 writeup/paper.tex
new quality data

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-hitlang}
\caption{Translation quality of by source language}
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Measured in this way, the average quality score across all HITs was just under 0.3. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-hitlang-new}
\caption{Translation quality of by source language}
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Measured in this way, the average quality score across all HITs was just under \textbf{XXXX}. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-new}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
